### 2015-03-30 README.Rmd
small edits to readme. and moved where some files are being sourced(). model does not run: problem is that in the function PopulateNet() on line 34 of file populate_net.R a variable called 'burn.in' is passed into a function but this variable is not defined as an arg to PopulateNet() or inside PopulateNet().

Martin Van der Linden and John Nay

Vanderbilt University

Master is the main script that sources everything else.
```{r, eval=FALSE, include=TRUE}
source(master.R)
````

>>>>

[Martin Van der Linden](https://martinvdlinden.wordpress.com/) (Dept. of Economics, Vanderbilt University) and [John Nay](https://johnnay.github.io) (School of Engineering, Vanderbilt University).

Master is the main script that sources everything else.
```{r, eval=FALSE, include=TRUE}
source("master.R")
````
